Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-08 tese2/13_implementation_model.tex
[ADD] speech detection

During a conversation, users may allow sharing their web cameras, by doing so their video is stored in recording chunks. Each chunk represents an interval of time  $T=\big[c^{start},c^{end}\big[$, it contains a reference to a group and a mapping between entity that was recorded and the correspondent video \ac{URL}.

>>>>

During a conversation, users may allow sharing their web cameras, by doing so their video is stored in recording chunks. Each chunk represents an interval of time  $T=\big[c^{start},c^{end}\big[$, it contains a reference to a group and list of \ac{URL}s with the correspondent owner identification number and \emph{WebSocket} session id.

In order to allow different devices within the same user, storing just the \ac{URL} with an associated user id is not enough as in this case it is needed one more parameter to differentiate the different \emph{webSocket} sessions opened by the same user. For this reason we had to associate a random session identification number to each \emph{webSocket}.

### 2016-04-08 tese2/16_implementation_content.tex
[ADD] speech detection

>>>>

	\subsection{Switching views}

		We provide a way for users to select the composite view of the conference room or the video shared by a particular user device as it can be seen on figure \ref{fig:devices}.

		In order to maintain a list of available user devices that can be played at the navigated time if a user plays or ends playing a block of recorded video it obtains at the same time a list of all devices available for each user at that time.

		On the other hand, if a user changes to real time, the list of devices is extracted from the set of \emph{webSockets} that are associated to the respective conference room. This list of devices is also sent to the users that are also in real time mode whenever a new user enters or leaves the conference room.

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.8\textwidth]{figures/devices.png}
		\caption{Multiple devices per user}
		\label{fig:devices}
	\end{figure}

		We also provide an automatic mechanism for switching the view to the current speaker. With respect to sound analysis, the sound samples are analyzed on the client side through the web audio \ac{API}.

		Our speech detector is straightforward, we could perform a spectral analysis in order to understand if the analyzed sound contains frequencies in the range of the human voice but instead we just capture sound samples in real time and calculate the maximum sound amplitude. If a sound sample has an amplitude bigger than a factor of the maximum amplitude (we have used an empirical value of 10\%) we say that the user is speaking and therefore we send a message to the server if the speaking state has changed. Subsequently, the server receives the user speaking state and sends it to the other users so they can request a different view.

### 2016-04-08 tese2/evaluation.tex
[ADD] speech detection

Figure \ref{fig:test_full_features_cpu} shows the percentage of \ac{CPU} usage during our performance test case. As we can see, the amount of \ac{CPU} increases and decreases linearly in function of the amount of conference participants.

>>>>

Figure \ref{fig:test_full_features_cpu} shows the percentage of \ac{CPU} usage during our performance test case. Each 100\% represents one \ac{CPU} core, although that does not mean one \ac{CPU} is fully used, for example two cores at 60\% represent 120\% \ac{CPU} usage. As we can see, the percentage of \ac{CPU} used increases and decreases linearly in function of the amount of conference participants.

### 2016-04-08 tese2/stats/summary_full_cpu.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1200,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

		\addplot[color=Blue] table[x expr=\thisrowno{0}-122,y index=1] {stats/summary_full_cpu_mongo.dat};
		\addlegendentry{Mongod}

		\addplot[color=Red] table[x expr=\thisrowno{0}-122,y index=1] {stats/summary_full_cpu_kms.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[color=Green] table[x expr=\thisrowno{0}-122,y index=1] {stats/summary_full_cpu_kr.dat};
		\addlegendentry{Kurento Repository}

		\addplot[color=Magenta] table[x expr=\thisrowno{0}-122,y index=1] {stats/summary_full_cpu_play.dat};
		\addlegendentry{Java}

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1200,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

		\addplot[color=Blue] table[x expr=\thisrowno{0}-122,y index=1] {stats/test_full_features/summary_cpu_mongo.dat};
		\addlegendentry{Mongod}

		\addplot[color=Red] table[x expr=\thisrowno{0}-122,y index=1] {stats/test_full_features/summary_cpu_kms.dat};
		\addlegendentry{Kurento Media Server}

		\addplot[color=Green] table[x expr=\thisrowno{0}-122,y index=1] {stats/test_full_features/summary_cpu_kr.dat};
		\addlegendentry{Kurento Repository}

		\addplot[color=Magenta] table[x expr=\thisrowno{0}-122,y index=1] {stats/test_full_features/summary_cpu_play.dat};
		\addlegendentry{Java}

### 2016-04-08 tese2/stats/summary_full_net.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [mbps]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=10,
	    xtick={0,60,...,2000},
	    ytick={0,1,...,100},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [mbps]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=10,
	    xtick={0,60,...,2000},
	    ytick={0,1,...,100},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_client_net.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [kbps]},
	    xmin=-10, xmax=790,
	    ymin=0, ymax=1000,
	    xtick={0,60,...,2000},
	    ytick={0,100,...,5000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [kbps]},
	    xmin=-10, xmax=790,
	    ymin=0, ymax=1000,
	    xtick={0,60,...,2000},
	    ytick={0,100,...,5000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_full_features_cpu.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1200,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1200,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_full_features_cpu_zoom.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=100,
	    xtick={0,60,...,2000},
	    ytick={0,20,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=100,
	    xtick={0,60,...,2000},
	    ytick={0,20,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_full_features_mem.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1800,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=1800,
	    xtick={0,60,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_full_features_net.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [mbps]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=25,
	    xtick={0,60,...,2000},
	    ytick={0,5,...,100},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Network usage},
	    xlabel={Time [seconds]},
	    ylabel={Transfer rate [mbps]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=25,
	    xtick={0,60,...,2000},
	    ytick={0,5,...,100},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_hour_cpu.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=0, xmax=3600,
	    ymin=0, ymax=1000,
	    xtick={0,500,...,5000},
	    ytick={0,100,...,2000},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=0, xmax=3600,
	    ymin=0, ymax=1000,
	    xtick={0,500,...,5000},
	    ytick={0,100,...,2000},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_hour_mem.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=0, xmax=3600,
	    ymin=0, ymax=4000,
	    xtick={0,500,...,5000},
	    ytick={0,500,...,4000},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=0, xmax=3600,
	    ymin=0, ymax=4000,
	    xtick={0,500,...,5000},
	    ytick={0,500,...,4000},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_two_times_cpu.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=1690,
	    ymin=0, ymax=1200,
	    xtick={0,120,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=1690,
	    ymin=0, ymax=1200,
	    xtick={0,120,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_two_times_mem.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=1690,
	    ymin=0, ymax=1800,
	    xtick={0,120,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Memory Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=1690,
	    ymin=0, ymax=1800,
	    xtick={0,120,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={0,60,...,2000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_without_qrcode_cpu.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=600,
	    xtick={0,100,...,2000},
	    ytick={0,100,...,2000},
	    extra x ticks={10,70,...,1000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={CPU usage},
	    xlabel={Time [seconds]},
	    ylabel={CPU [percentage]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=600,
	    xtick={0,100,...,2000},
	    ytick={0,100,...,2000},
	    extra x ticks={10,70,...,1000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

### 2016-04-08 tese2/stats/test_without_qrcode_mem.tex
[ADD] speech detection

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=6cm,
	    title={Mem Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=2000,
	    xtick={0,100,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={10,70,...,1000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]

>>>>

\begin{tikzpicture}
	\begin{axis}[
	    width=\textwidth,
	   	height=8cm,
	    title={Mem Usage},
	    xlabel={Time [seconds]},
	    ylabel={Memory [MB]},
	    xmin=-10, xmax=850,
	    ymin=0, ymax=2000,
	    xtick={0,100,...,2000},
	    ytick={0,200,...,2000},
	    extra x ticks={10,70,...,1000},
    	extra x tick labels={,,},
		extra tick style={
			grid=major,
			major grid style={yellow,thick,solid},
			tick label style={rotate=90,anchor=east}
		},
     legend cell align=left,
     legend style={legend pos=north west,font=\tiny},
	    ymajorgrids=true,
	    grid style=dashed,
	]
